---
title: 'Pollimetry: Predictive allometry for pollinating insects'
author: "Liam Kendall, Ignasi Bartomeus, Vesna Gagic etc"
date: "22/04/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Nacho

If you could help me with setting up the data files within this R markdown file, I will write the manuscript in it!


Method

#Testing of key co-variates

Preservative time - in australia only

Bio region - included in analysis as considered key 

Latitude -- still very unsure about this, more likely a sampling relic 


#Sampling co-variates

Measurement - Included as random effect, the measurer + instrument (incl instruments used).



#Model choice


#Model validation

I read a forum post about how AIC === cross-validation / i.e. one in the same, however I still like cross-validation so i think we should use MCMCglmm (package name and fnction)- for reasons I will explain later

#Where this paper is going?

Phylogeny is key here - I think we present empirical data from arond the world with simple IT~Spec.weight output

And then use Nico's input to focus largely on phylogeny - I am finding phylo singal (Pagel's lambda) very high but there are methodological considerations I cannot fix yet
  - whether or not the tree used is ultrametric or not
  - including subgenera - binding trees where phylogeny is well-resolved i.e. adding bombus tree would be ace
  - making MCMCglmm do PGLS, i have numerous errors so ive given up for now - wil talk with mol ecologist at       UNE
  














```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
