---
title: 'Pollimetry: Predictive allometry for pollinating insects'
author: "Liam Kendall, Vesna Gagic..........Romina Rader, Ignasi Bartomeus "
date: "24/04/2018"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Nacho

If you could help me with setting up the data files within this R markdown file, I will write the manuscript in it!

All below is about bees - waiting on species ids for aussie hoverflies but workflow will be the same!

#Testing of key co-variates

Preservative time - in australia only 
  - I think proper syntax is WEIGHT ~ SPECIES + PRES.TIME
  -See preservative time workflow file - 160 = -0.8mg - very insignificant
  
Bio region - included in analysis

I want to exclude latitude and climate - i see these impacts more likely to be sampling relics, although perhaps we can test in europe once we have belgian data!!!?

Intraspecific variation - done for five most speciose species

#Sampling co-variates

Measurement - Included as random effect, the measurer + instrument so my measurements in Aus and Switz are two different levels.

#Model choice

See workflowLK.R

-done

#Model validation

I read a forum post about how AIC === cross-validation / i.e. one in the same, however I still like cross-validation so i think we should use MCMCglmm (package name and function)- as we cna use it for validation and it also allows inclusion of phylogeny

-Have tried using MCMCglmm for non-phylo model too - i think maybe we should just use both for final model? 
But use lmer for model selection? Dredge doesnt accept MCMC

See MCMCglmm.R for this

#Where this paper is going?

SEE PGLS_workflow.R

I think we are going to find a big section on phylogeny given my initial PGLS results. I think there is considerable signal in the IT~weight relationship and Spec.wgt in particular. As such, we need to make sure we use the right phylogeny.

Perhaps use Nico's input to focus largely on phylogeny - I am finding phylo singal (Pagel's lambda) very high but there are methodological considerations I cannot fix yet
  - whether or not the tree used is ultrametric or not
  - including subgenera - binding trees where phylogeny is well-resolved i.e. adding bombus tree would be ace
  - making MCMCglmm do PGLS, i have numerous errors so ive given up for now - wil talk with a mol ecologist at       UNE and see if i can find some help.
=======

Method

#Testing of key co-variates

Preservative time - in australia only

Bio region - included in analysis as considered key 

Latitude -- still very unsure about this, more likely a sampling relic 


#Sampling co-variates

Measurement - Included as random effect, the measurer + instrument (incl instruments used).



#Model choice


#Model validation

I read a forum post about how AIC === cross-validation / i.e. one in the same, however I still like cross-validation so i think we should use MCMCglmm (package name and fnction)- for reasons I will explain later

#Where this paper is going?

Phylogeny is key here - I think we present empirical data from arond the world with simple IT~Spec.weight output

And then use Nico's input to focus largely on phylogeny - I am finding phylo singal (Pagel's lambda) very high but there are methodological considerations I cannot fix yet
  - whether or not the tree used is ultrametric or not
  - including subgenera - binding trees where phylogeny is well-resolved i.e. adding bombus tree would be ace
  - making MCMCglmm do PGLS, i have numerous errors so ive given up for now - wil talk with mol ecologist at       UNE












```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
