---
title: 'Pollimetry: Predictive allometry for pollinating insects'
author: "Liam Kendall, Vesna Gagic..........Romina Rader and Ignasi Bartomeus"
date: "24/04/2018"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(broom)
library(lme4)
library(phytools)
library(nlme)
library(phangorn)
library(ggtree)
library(MuMIn)
library(geiger)
#dataframe
poll_all <- read.csv(file="data/PA28418.csv")

#split to bees and hoverflies
poll_all$Spec.wgt=poll_all$Spec.wgt*1000
poll_all_split=split(poll_all,poll_all$Superfamily)
bee_all=poll_all_split[[1]]

#JUST AUSTRALIA
bee_country=split(bee_all,bee_all$Country)
bee_australia=bee_country$Australia

#Filter so only species with more than 1 preservative time

bee_aus=as.data.frame(bee_australia %>%
  group_by(Species) %>% 
  filter(n_distinct(Pres.time)>1))
##BEE mean
bee_mean=aggregate(Latitude~Family+Subfamily+Tribe+Region+Country+Measurement+Subfamily+Genus+Species+Sex,bee_all,mean)
bee_mean$Spec.wgt=as.numeric(unlist(aggregate(Spec.wgt~Family+Country+Subfamily+Tribe+Region+Measurement+
                                                Subfamily+Genus+Species+Sex,bee_all,mean)[10]))
bee_mean$IT=(as.numeric(unlist(aggregate(IT~Family+Subfamily+Tribe+Region+Country+
                                         Measurement+Subfamily+Genus+Species+Sex,bee_all,mean)[10])))


##Top five - for intraspecific variance
bee_species=split(bee_all,bee_all$Species)

bee_phylo=aggregate(Latitude~Family+Subfamily+
                      Tribe+Genus+Species,bee_all,median)
bee_phylo$Longitude=as.numeric(unlist(aggregate(Longitude~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,median)[6]))
bee_phylo$Spec.wgt=as.numeric(unlist(aggregate(Spec.wgt~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,mean)[6]))
bee_phylo$Wgt.SD=as.numeric(unlist(aggregate(log(Spec.wgt)~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,sd)[6]))
bee_phylo$IT=as.numeric(unlist(aggregate(IT~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,mean)[6]))
bee_phylo$IT.SD=as.numeric(unlist(aggregate(log(IT)~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,sd)[6]))
rownames(bee_phylo)=bee_phylo$Species

bee_phylo=bee_phylo[-93,]
##Build tree
##TREE
bee.phy=read.tree(file="raw_data/Bee_phylogeny_Hedtke_etal2013/12862_2013_2375_MOESM3_ESM.txt",keep.multi = TRUE)
##Use tree 1 (376 genera) #Genera-level phylogney
bee.phy=bee.phy[[1]]
bee.phy=as.phylo(bee.phy)
#bee.phy=force.ultrametric(bee.phy) Not sure if this is required
bee_pruned=drop.tip(bee.phy, setdiff(bee.phy$tip.label,bee_phylo$Genus))
bee_pruned=genus.to.species.tree(bee_pruned, species=bee_phylo$Species)


```

##Nacho

If you could help me with setting up the data files within this R markdown file, I will write the manuscript in it!

All below is about bees - waiting on species ids for aussie hoverflies but workflow will be the same!

#Method


#Model structure

We included 'measurement' which denoted the measurer as well as each instrument as a random term.

Measurement - Included as random effect, the measurer + instrument so my measurements in Aus and Switz are two different levels.

See workflowLK.R

-done


#Testing of key co-variates

#Preservative time - Australia only

We tested the effect of time in preservative (70-100% ethanol) on Australian bee samples.In total, we had nine bee species which had been subjected to different lengths within ethanol.

  - I think proper syntax is WEIGHT ~ SPECIES + PRES.TIME (or Species*Pres.time?) or WGT ~ Pres.time + (1|Species)?

Overall, preservative time accounted for a decrease in 0.005mg per day. 
  
```{r}
<<<<<<< HEAD

pres.lm=lm(Spec.wgt~Species+Pres.time,bee_aus)

summary(pres.lm)
```

```{r}
library(lme4)
pres.lme=lmer(Spec.wgt~Pres.time+(1|Species),bee_aus)

=======
library(dplyr)
library(broom)
library(lme4)
#dataframe
poll_all <- read.csv(file="data/PA28418.csv")

#split to bees and hoverflies
poll_all$Spec.wgt=poll_all$Spec.wgt*1000
poll_all_split=split(poll_all,poll_all$Superfamily)
bee_all=poll_all_split[[1]]

#JUST AUSTRALIS
bee_country=split(bee_all,bee_all$Country)
bee_australia=bee_country$Australia

#Filter so only species with more than 1 preservative time

bee_aus=as.data.frame(bee_australia %>%
  group_by(Species) %>% 
  filter(n_distinct(Pres.time)>1))

pres.lm=lm(Spec.wgt~Species+Pres.time,bee_aus)

summary(pres.lm)
```

```{r}
library(lme4)
pres.lme=lmer(Spec.wgt~Pres.time+(1|Species),bee_aus)

>>>>>>> 5794288ddca0a6aa4b1e4e5ec8050ad63b1556a8
summary(pres.lme)
```

#Model choice

Test lme models /w and /wo biogeography.

#With region
```{r}
<<<<<<< HEAD

=======
library(MuMIn)

bee_mean=aggregate(Latitude~Family+Subfamily+Tribe+Region+Country+Measurement+Subfamily+Genus+Species+Sex,bee_all,mean)
bee_mean$Spec.wgt=as.numeric(unlist(aggregate(Spec.wgt~Family+Country+Subfamily+Tribe+Region+Measurement+
                                                Subfamily+Genus+Species+Sex,bee_all,mean)[10]))
bee_mean$IT=(as.numeric(unlist(aggregate(IT~Family+Subfamily+Tribe+Region+Country+
                                         Measurement+Subfamily+Genus+Species+Sex,bee_all,mean)[10])))
>>>>>>> 5794288ddca0a6aa4b1e4e5ec8050ad63b1556a8
######

bee_f_lme=lmer(log(Spec.wgt) ~ log(IT)  + Family + Sex + Region + #fix factors
                              log(IT):Family + log(IT):Region + log(IT):Sex + #interactions
                              (1|Measurement),REML=FALSE,bee_mean)
options(na.action = "na.fail")
bee_dr_lme=dredge(bee_f_lme,beta="none",rank="AIC",
              trace=10) #think about "sd" and "AICc". AIC show same pattern.
head(bee_dr_lme)


```
#Without region

```{r}
<<<<<<< HEAD
=======
##Data frame
poll_all <- read.csv(file="data/PA28418.csv")

#split to bees and hoverflies
poll_all$Spec.wgt=poll_all$Spec.wgt*1000
poll_all_split=split(poll_all,poll_all$Superfamily)
bee_all=poll_all_split[[1]]

options(na.action = "na.omit")

bee_mean=aggregate(Latitude~Family+Subfamily+Tribe+Region+Country+Measurement+Subfamily+Genus+Species+Sex,bee_all,mean)
bee_mean$Spec.wgt=as.numeric(unlist(aggregate(Spec.wgt~Family+Country+Subfamily+Tribe+Region+Measurement+
                                                Subfamily+Genus+Species+Sex,bee_all,mean)[10]))
bee_mean$IT=(as.numeric(unlist(aggregate(IT~Family+Subfamily+Tribe+Region+Country+
                                         Measurement+Subfamily+Genus+Species+Sex,bee_all,mean)[10])))
######
>>>>>>> 5794288ddca0a6aa4b1e4e5ec8050ad63b1556a8

bee_f_lme_red=lmer(log(Spec.wgt) ~ log(IT)  + Family + Sex  + #fix factors
                 log(IT):Family + log(IT):Sex + #interactions
                 (1|Measurement),REML=FALSE,bee_mean)

options(na.action = "na.fail")
bee_dr_lme_red=dredge(bee_f_lme_red,beta="none",rank="AIC",
              trace=10) #think about "sd" and "AICc". AIC show same pattern.
head(bee_dr_lme_red)


```

In both cases, the full model is retained. However, the difference in AIC is considerable (421.9 /w region vs. 479 /wo).

I want to exclude latitude and climate - i see these impacts more likely to be sampling relics.

Let us test this for Europe once we have belgian data as we will have good range.

<<<<<<< HEAD
=======
#Phylogenetic GLS

Here we can do two things: 1) check traits themselves and Wgt~IT, and 2) run with intraspecific variation for species we have more than one specimen (pgls.Ives (phytools))

```{r}
library(phytools)
library(nlme)
library(phangorn)
library(ggtree)
##Data frame
poll_all <- read.csv(file="data/PA28418.csv")

#split to bees and hoverflies
poll_all$Spec.wgt=poll_all$Spec.wgt*1000
poll_all_split=split(poll_all,poll_all$Superfamily)
bee_all=poll_all_split[[1]]

bee_phylo=aggregate(Latitude~Family+Subfamily+
                      Tribe+Genus+Species,bee_all,median)
bee_phylo$Longitude=as.numeric(unlist(aggregate(Longitude~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,median)[6]))
bee_phylo$Spec.wgt=as.numeric(unlist(aggregate(Spec.wgt~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,mean)[6]))
bee_phylo$Wgt.SD=as.numeric(unlist(aggregate(log(Spec.wgt)~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,sd)[6]))
bee_phylo$IT=as.numeric(unlist(aggregate(IT~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,mean)[6]))
bee_phylo$IT.SD=as.numeric(unlist(aggregate(log(IT)~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,sd)[6]))
rownames(bee_phylo)=bee_phylo$Species

##Build tree
##TREE
bee.phy=read.tree(file="raw_data/Bee_phylogeny_Hedtke_etal2013/12862_2013_2375_MOESM3_ESM.txt",keep.multi = TRUE)
##Use tree 1 (376 genera) #Genera-level phylogney
bee.phy=bee.phy[[1]]
bee.phy=as.phylo(bee.phy)
#bee.phy=force.ultrametric(bee.phy) Not sure if this is required
bee_pruned=drop.tip(bee.phy, setdiff(bee.phy$tip.label,bee_phylo$Genus))
bee_pruned=genus.to.species.tree(bee_pruned, species=bee_phylo$Species)

p=ggtree((bee_pruned))
p + geom_tiplab(size=3)

```

##Individual traits
#Spec.wgt

```{r}
library(phytools)
library(nlme)
library(phangorn)
library(ggtree)
##Data frame
poll_all <- read.csv(file="data/PA28418.csv")

#split to bees and hoverflies
poll_all$Spec.wgt=poll_all$Spec.wgt*1000
poll_all_split=split(poll_all,poll_all$Superfamily)
bee_all=poll_all_split[[1]]

bee_phylo=aggregate(Latitude~Family+Subfamily+
                      Tribe+Genus+Species,bee_all,median)
bee_phylo$Longitude=as.numeric(unlist(aggregate(Longitude~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,median)[6]))
bee_phylo$Spec.wgt=as.numeric(unlist(aggregate(Spec.wgt~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,mean)[6]))
bee_phylo$Wgt.SD=as.numeric(unlist(aggregate(log(Spec.wgt)~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,sd)[6]))
bee_phylo$IT=as.numeric(unlist(aggregate(IT~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,mean)[6]))
bee_phylo$IT.SD=as.numeric(unlist(aggregate(log(IT)~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,sd)[6]))
rownames(bee_phylo)=bee_phylo$Species

bee_phylo=bee_phylo[-93,]
##TREE
bee.phy=read.tree(file="raw_data/Bee_phylogeny_Hedtke_etal2013/12862_2013_2375_MOESM3_ESM.txt",keep.multi = TRUE)
##Use tree 1 (376 genera) #Genera-level phylogeny
bee.phy=bee.phy[[1]]
bee.phy=as.phylo(bee.phy)
#bee.phy=force.ultrametric(bee.phy) Not sure if this is required
bee_pruned=drop.tip(bee.phy, setdiff(bee.phy$tip.label,bee_phylo$Genus))
bee_pruned=genus.to.species.tree(bee_pruned, species=bee_phylo$Species)

#first compute correlation matrix from tree
Bee_vcv=corPagel(value=0.5,phy=bee_pruned,fixed=FALSE)

WGT_GLS1<- gls(log(Spec.wgt)~1, data=bee_phylo, method="ML")
WGT_PGLS1 = gls(log(Spec.wgt)~1, data=bee_phylo, correlation=Bee_vcv, method="ML")



AIC(WGT_GLS1,WGT_PGLS1)
summary(WGT_PGLS1)

```


##Intertegular distance

```{r}
library(phytools)
library(nlme)
library(phangorn)
library(ggtree)
##Data frame
poll_all <- read.csv(file="data/PA28418.csv")

#split to bees and hoverflies
poll_all$Spec.wgt=poll_all$Spec.wgt*1000
poll_all_split=split(poll_all,poll_all$Superfamily)
bee_all=poll_all_split[[1]]

bee_phylo=aggregate(Latitude~Family+Subfamily+
                      Tribe+Genus+Species,bee_all,median)
bee_phylo$Longitude=as.numeric(unlist(aggregate(Longitude~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,median)[6]))
bee_phylo$Spec.wgt=as.numeric(unlist(aggregate(Spec.wgt~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,mean)[6]))
bee_phylo$Wgt.SD=as.numeric(unlist(aggregate(log(Spec.wgt)~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,sd)[6]))
bee_phylo$IT=as.numeric(unlist(aggregate(IT~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,mean)[6]))
bee_phylo$IT.SD=as.numeric(unlist(aggregate(log(IT)~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,sd)[6]))
rownames(bee_phylo)=bee_phylo$Species

bee_phylo=bee_phylo[-93,]
##TREE
bee.phy=read.tree(file="raw_data/Bee_phylogeny_Hedtke_etal2013/12862_2013_2375_MOESM3_ESM.txt",keep.multi = TRUE)
##Use tree 1 (376 genera) #Genera-level phylogeny
bee.phy=bee.phy[[1]]
bee.phy=as.phylo(bee.phy)
#bee.phy=force.ultrametric(bee.phy) Not sure if this is required
bee_pruned=drop.tip(bee.phy, setdiff(bee.phy$tip.label,bee_phylo$Genus))
bee_pruned=genus.to.species.tree(bee_pruned, species=bee_phylo$Species)

#first compute correlation matrix from tree
Bee_vcv=corPagel(value=0.5,phy=bee_pruned,fixed=FALSE)

IT_GLS1<- gls(log(IT)~1, data=bee_phylo, method="ML")
IT_PGLS1 = gls(log(IT)~1, data=bee_phylo, correlation=Bee_vcv, method="ML")



AIC(IT_GLS1,IT_PGLS1)
summary(IT_PGLS1)

```


##Predictive model
#SPEC.WGT ~ IT


```{r}
library(phytools)
library(nlme)
library(phangorn)
library(ggtree)
##Data frame
poll_all <- read.csv(file="data/PA28418.csv")

#split to bees and hoverflies
poll_all$Spec.wgt=poll_all$Spec.wgt*1000
poll_all_split=split(poll_all,poll_all$Superfamily)
bee_all=poll_all_split[[1]]

bee_phylo=aggregate(Latitude~Family+Subfamily+
                      Tribe+Genus+Species,bee_all,median)
bee_phylo$Longitude=as.numeric(unlist(aggregate(Longitude~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,median)[6]))
bee_phylo$Spec.wgt=as.numeric(unlist(aggregate(Spec.wgt~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,mean)[6]))
bee_phylo$Wgt.SD=as.numeric(unlist(aggregate(log(Spec.wgt)~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,sd)[6]))
bee_phylo$IT=as.numeric(unlist(aggregate(IT~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,mean)[6]))
bee_phylo$IT.SD=as.numeric(unlist(aggregate(log(IT)~Family+Subfamily+
                                      Tribe+Genus+Species,bee_all,sd)[6]))
rownames(bee_phylo)=bee_phylo$Species

bee_phylo=bee_phylo[-93,]
##TREE
bee.phy=read.tree(file="raw_data/Bee_phylogeny_Hedtke_etal2013/12862_2013_2375_MOESM3_ESM.txt",keep.multi = TRUE)
##Use tree 1 (376 genera) #Genera-level phylogeny
bee.phy=bee.phy[[1]]
bee.phy=as.phylo(bee.phy)
#bee.phy=force.ultrametric(bee.phy) Not sure if this is required
bee_pruned=drop.tip(bee.phy, setdiff(bee.phy$tip.label,bee_phylo$Genus))
bee_pruned=genus.to.species.tree(bee_pruned, species=bee_phylo$Species)

#first compute correlation matrix from tree
Bee_vcv=corPagel(value=0.5,phy=bee_pruned,fixed=FALSE)

Bee_GLS1<- gls(log(Spec.wgt)~log(IT), data=bee_phylo, method="ML")
summary(Bee_GLS1)

Bee_PGLS1 = gls(log(Spec.wgt)~log(IT), data=bee_phylo, correlation=Bee_vcv, method="ML")
summary(Bee_PGLS1)

AIC(Bee_GLS1,Bee_PGLS1)


```

Together, low lambda (not sure if we should be used lambda) but good result nonetheless. Suggests a non-PGLS model is best for predicting body size even if both BS and IT have phylo-signal.

>>>>>>> 5794288ddca0a6aa4b1e4e5ec8050ad63b1556a8
##Intraspecific variation

Plotted for five most speciose species: Homalictus_urbanus, Lasioglossum_pauxillum, Bombus_lucorum, Andrena_flavipes and Lasioglossum_lanarium

```{r}
<<<<<<< HEAD
=======
##Data frame
poll_all <- read.csv(file="data/PA28418.csv")

#split to bees and hoverflies
poll_all$Spec.wgt=poll_all$Spec.wgt*1000
poll_all_split=split(poll_all,poll_all$Superfamily)
bee_all=poll_all_split[[1]]

##Top five
bee_species=split(bee_all,bee_all$Species)

>>>>>>> 5794288ddca0a6aa4b1e4e5ec8050ad63b1556a8
#Homalictus_urbanus
#Lasioglossum_pauxillum
#Bombus_lucorum
#Andrena_flavipes
#Lasioglossum_lanarium


##ONE##
#Homalictus_urbanus
#IT
HU_IT = c()
for(i in 1:length(bee_species$Homalictus_urbanus$IT)){
  subset1 = sample(bee_species$Homalictus_urbanus$IT, i)
  HU_IT[i] = mean(subset1)
}

#Specimen weight
HU_WT = c()
for(i in 1:length(bee_species$Homalictus_urbanus$Spec.wgt)){
  subset1 = sample(bee_species$Homalictus_urbanus$Spec.wgt, i)
  HU_WT[i] = mean(subset1)
}


##TWO##

#Lasioglossum_pauxillum
#IT
LP_IT = c()
for(i in 1:length(bee_species$Lasioglossum_pauxillum$IT)){
  subset1 = sample(bee_species$Lasioglossum_pauxillum$IT, i)
  LP_IT[i] = mean(subset1)
}

#Specimen weight
LP_WT = c()
for(i in 1:length(bee_species$Lasioglossum_pauxillum$Spec.wgt)){
  subset1 = sample(bee_species$Lasioglossum_pauxillum$Spec.wgt, i)
  LP_WT[i] = mean(subset1)
}

##THREE
#Bombus_lucorum
BL_IT = c()
for(i in 1:length(bee_species$Bombus_lucorum$IT)){
  subset1 = sample(bee_species$Bombus_lucorum$IT, i)
  BL_IT[i] = mean(subset1)
}

#Specimen weight
BL_WT = c()
for(i in 1:length(bee_species$Bombus_lucorum$Spec.wgt)){
  subset1 = sample(bee_species$Bombus_lucorum$Spec.wgt, i)
  BL_WT[i] = mean(subset1)
}

##FOUR##
#Andrena_flavipes
#IT
AF_IT = c()
for(i in 1:length(bee_species$Andrena_flavipes$IT)){
  subset1 = sample(bee_species$Andrena_flavipes$IT, i)
  AF_IT[i] = mean(subset1)
}

#Specimen weight
AF_WT = c()
for(i in 1:length(bee_species$Andrena_flavipes$Spec.wgt)){
  subset1 = sample(bee_species$Andrena_flavipes$Spec.wgt, i)
  AF_WT[i] = mean(subset1)
}

##FIVE##
#Lasioglossum_lanarium
LL_IT = c()
for(i in 1:length(bee_species$Lasioglossum_lanarium$IT)){
  subset1 = sample(bee_species$Lasioglossum_lanarium$IT, i)
  LL_IT[i] = mean(subset1)
}


#Specimen weight
LL_WT = c()
for(i in 1:length(bee_species$Lasioglossum_lanarium$Spec.wgt)){
  subset1 = sample(bee_species$Lasioglossum_lanarium$Spec.wgt, i)
  LL_WT[i] = mean(subset1)
}

<<<<<<< HEAD
##graphed three for aesthetics based on size range
par(mfrow=c(2,3))
par(pty="s")
plot(HU_IT,main="Homalictus urbanus",ylab = "ITD (mm)",xlab="")
#plot(LP_IT,main="Lasioglossum pauxillum",ylab = "",xlab="")
plot(AF_IT,main="Andrena flavipes",ylab = "",xlab="Sample size")
plot(BL_IT,main="Bombus lucorum",ylab = "",xlab="")

#plot(LL_IT,main="Lasioglossum lanarium",ylab = "",xlab="Sample size")

plot(HU_WT,ylab = "Specimen weight (mg)",xlab="Sample size")
#plot(LP_WT,ylab = "",xlab="Sample size")
plot(AF_WT,ylab = "",xlab="Sample size")
plot(BL_WT,ylab = "",xlab="Sample size")

#plot(LL_WT,ylab = "",xlab="Sample size")
=======

par(mfrow=c(2,5))
par(pty="s")
plot(HU_IT)
plot(LP_IT)
plot(BL_IT)
plot(AF_IT)
plot(LL_IT)

plot(HU_WT)
plot(LP_WT)
plot(BL_WT)
plot(AF_WT)
plot(LL_WT)
>>>>>>> 5794288ddca0a6aa4b1e4e5ec8050ad63b1556a8
```


#Model validation

##Training and test set

##Bootstrap - not currently possible for lme so back to train/test

```{r}
library(ModelMetrics)
set.seed(123)
bee_subset=sample(seq_len(nrow(bee_mean)), size = floor(0.8 * nrow(bee_mean)))
bee_test <- bee_mean[-bee_subset, ]
bee_train <- bee_mean[bee_subset, ]

<<<<<<< HEAD
Cane <- function(IT){exp(0.6453 + 2.4691*log(IT))}
=======
>>>>>>> 5794288ddca0a6aa4b1e4e5ec8050ad63b1556a8

bee_test_mod=lmer(log(Spec.wgt) ~ log(IT)  + Family + Sex + Region + #fix factors
                              log(IT):Family + log(IT):Region + log(IT):Sex + #interactions
                              (1|Measurement),data=bee_train,REML=FALSE)
bee_test_red_mod=lmer(formula = log(Spec.wgt) ~ log(IT) + Family + Sex + log(IT):Family + 
    log(IT):Sex + (1 | Measurement), data = bee_train, REML = FALSE)

<<<<<<< HEAD
bee_test_red_mod2=lmer(formula = log(Spec.wgt) ~ log(IT) + (1 | Measurement), data = bee_train, REML = FALSE)

bee_pred1=predict(bee_test_mod,newdata=bee_test)
bee_pred2=predict(bee_test_red_mod,newdata=bee_test)
bee_pred3=predict(bee_test_red_mod2,newdata=bee_test)
bee_pred4=0.6453 + 2.4691*log(bee_test$IT)
par(pty="s")
plot(log(Spec.wgt)~log(IT),bee_train,ylab="lnSpecimen weight (mg)",xlab="lnITD (mm)")
points(bee_pred1~log(bee_test$IT),col=2)
points(bee_pred2~log(bee_test$IT),col=3)
points(bee_pred3~log(bee_test$IT),col=4)
points(bee_pred4~log(bee_test$IT),col=5)

bee_rmse=cbind(
rmse(log(bee_test$Spec.wgt),bee_pred1),
rmse(log(bee_test$Spec.wgt),bee_pred2),
rmse(log(bee_test$Spec.wgt),bee_pred3),
rmse(log(bee_test$Spec.wgt),bee_pred4))
colnames(bee_rmse)=c("Full","Reduced","IT","Cane")
rownames(bee_rmse)=c("RMSE")
bee_rmse
```
=======
bee_pred1=predict(bee_test_mod,newdata=bee_test)
bee_pred2=predict(bee_test_red_mod,newdata=bee_test)

par(pty="s")
plot(log(Spec.wgt)~log(IT),bee_train,ylab="lnSpecimen weight (mg)",xlab="lnITD (mm)")
points(bee_pred1~log(bee_test$IT),col=2)
points(bee_pred2~log(bee_test$IT),col=3)

rmse(log(bee_test$Spec.wgt),bee_pred1)#0.007
rmse(log(bee_test$Spec.wgt),bee_pred2)

```

>>>>>>> 5794288ddca0a6aa4b1e4e5ec8050ad63b1556a8


Cane is good, ours is slightly better - good validation of Cane though!! Our data captures natural variability and slight differences between families esp. Apidae vs. the rest

Dan is providing data in next couple of weeks.

I think phylo-signal of body size / IT is cool / interesting angle. Not sure if individual traits need to be log-transformed for signal

Perhaps use Nico's input for focus on phylogeny - I am finding phylo singal (Pagel's lambda) is high but there are methodological considerations I cannot fix yet
  - whether or not the tree used is ultrametric or not
  - including subgenera - binding trees where phylogeny is well-resolved i.e. adding bombus tree would be ace - from my understanding lambda is robust to this

Here we can do two things: 1) check traits themselves and Wgt~IT, and 2) run with intraspecific variation for species we have more than one specimen (pgls.Ives (phytools)) - still working this out - it has annoying input but so does geiger



```{r}
library(phytools)
library(nlme)
library(phangorn)
library(ggtree)
##Data frame
poll_all <- read.csv(file="data/PA28418.csv")

#split to bees and hoverflies
poll_all$Spec.wgt=poll_all$Spec.wgt*1000
poll_all_split=split(poll_all,poll_all$Superfamily)
bee_all=poll_all_split[[1]]


p=ggtree((bee_pruned))
p + geom_tiplab(size=3)

```

##Individual traits PIC
#Spec.wgt

```{r}

bee_phylo_WGT=as.data.frame(bee_phylo[,c("Spec.wgt")])
rownames(bee_phylo_WGT)=rownames(bee_phylo)

wgt_geig=fitContinuous(bee_pruned, bee_phylo_WGT,SE=0,
              model = c("lambda"))
wgt_geig

wgt_geig_log=fitContinuous(bee_pruned, log(bee_phylo_WGT),SE=0,
              model = c("lambda"))
wgt_geig_log
```

##Intertegular distance
```{r}

bee_phylo_IT=as.data.frame(bee_phylo[,c("IT")])
rownames(bee_phylo_IT)=rownames(bee_phylo)

it_geig=fitContinuous(bee_pruned, bee_phylo_IT,SE=0,
              model = c("lambda"))
it_geig

it_geig_log=fitContinuous(bee_pruned, log(bee_phylo_IT),SE=0,
              model = c("lambda"))
it_geig_log
```


##Predictive model
#SPEC.WGT ~ IT

```{r}

#first compute correlation matrix from tree
Bee_vcv=corPagel(value=0.5,phy=bee_pruned,fixed=FALSE)

Bee_GLS1<- gls(log(Spec.wgt)~log(IT), data=bee_phylo, method="ML")
summary(Bee_GLS1)

Bee_PGLS1 = gls(log(Spec.wgt)~log(IT), data=bee_phylo, correlation=Bee_vcv, method="ML")
summary(Bee_PGLS1)

AIC(Bee_GLS1,Bee_PGLS1)


```

Together, lower lambda (ln Wgt~ln IT) but good result nonetheless. 

Suggests a non-PGLS model is best for predicting body size even if both BS and IT have strong phylo-signal. - multiple methods (geiger (PIC) and PGLS intercept models)


#####Hoverflies

```{r}
hov_all=poll_all_split[[2]]

options(na.action=na.omit)
hov_mean=aggregate(Latitude~Family+Tribe+Country+
                     Region+Measurement+Subfamily+Genus+Species+Sex,hov_all,mean)
hov_mean$Longitude=aggregate(Longitude~Family+Tribe+Country+
                     Region+Measurement+Subfamily+Genus+Species+Sex,hov_all,mean)[10]

hov_mean$Spec.wgt=as.numeric(unlist(aggregate(Spec.wgt~Family+Tribe+Country+
                                                Region+Measurement+Subfamily+
                                                Genus+Species+Sex,hov_all,mean)[10]))
hov_mean$IT=as.numeric(unlist(aggregate(IT~Family+Tribe+Country+
                                          Region+Measurement+Subfamily+
                                          Genus+Species+Sex,hov_all,mean)[10]))
##Full
hov.full=lmer(log(Spec.wgt) ~ log(IT) + Region+ Sex + Subfamily+ #fix
            log(IT):Sex + #interactions
            log(IT):Subfamily + log(IT):Region+ (1|Measurement)
            ,REML=FALSE,data=hov_mean)
##/wo region
hov.red=lmer(log(Spec.wgt) ~ log(IT) + Sex + Subfamily+ #fix
            log(IT):Sex + #interactions
            log(IT):Subfamily + (1|Measurement)
            ,REML=FALSE,data=hov_mean)

##DREDGE
options(na.action = "na.fail")

hov_dr=dredge(hov.full,beta="none",rank="AIC",
              trace=100) #think about "sd" and "AICc". AIC show same pattern.
head(hov_dr)

hov_dr_red=dredge(hov.red,beta="none",rank="AIC",
              trace=100) #think about "sd" and "AICc". AIC show same pattern.
head(hov_dr_red)
```

#Model validation - hoverflies

##Training and test set

##Bootstrap - not currently possible for lme so back to train/test

```{r}
library(ModelMetrics)
set.seed(123)
hov_subset=sample(seq_len(nrow(hov_mean)), size = floor(0.8 * nrow(hov_mean)))
hov_test <- hov_mean[-hov_subset, ]
hov_train <- hov_mean[hov_subset, ]

hov_test_mod=lmer(formula = log(Spec.wgt) ~ log(IT) + Region + Sex + Subfamily + 
    log(IT):Sex + log(IT):Subfamily + log(IT):Region + (1 | Measurement), 
    data = hov_train, REML = FALSE)
hov_test_red_mod=lmer(formula = log(Spec.wgt) ~ log(IT) + Sex + Subfamily + log(IT):Sex + 
    log(IT):Subfamily + (1 | Measurement), data = hov_train, REML = FALSE)

hov_test_red_mod2=lmer(formula = log(Spec.wgt) ~ log(IT) + (1 | Measurement), data = hov_train, REML = FALSE)

hov_pred1=predict(hov_test_mod,newdata=hov_test)
hov_pred2=predict(hov_test_red_mod,newdata=hov_test)
hov_pred3=predict(hov_test_red_mod2,newdata=hov_test)

par(pty="s")
plot(log(Spec.wgt)~log(IT),hov_train,ylab="ln Specimen weight (mg)",xlab="ln ITD (mm)")
points(hov_pred1~log(hov_test$IT),col=2)
points(hov_pred2~log(hov_test$IT),col=3)
points(hov_pred3~log(hov_test$IT),col=4)

rmse(log(hov_test$Spec.wgt),hov_pred1)
rmse(log(hov_test$Spec.wgt),hov_pred2)
rmse(log(hov_test$Spec.wgt),hov_pred3)

```


##Intraspecific variation in hoverflies